On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-29 paper/paper.tex
A small table connecting Church encoding section back to the rest of the paper

\subsection{Connection to Church encodings}
\begin{todo}
  Work on this subsection. Maybe this shouldn't be a separate section at all and
  maybe its contents should be incorporated throughout the rest of the paper.
\end{todo}

@@

>>>>

\subsection{Connection to Church encodings}
% \begin{todo}
%   Work on this subsection. Maybe this shouldn't be a separate section at all and
%   maybe its contents should be incorporated throughout the rest of the paper.
% \end{todo}

@@

The \verb|Church'| type forms a large part of the foundation of the pattern
matching aspect of the \verb|E| type. A correspondence between the two
is given in the table below.\\

{\small
\noindent\begin{tabular}{|p{3.4cm}|p{4.4cm}|}
  \hline
  \ttt{Church' (a, b) r} & \ttt{E (SumMatch (a, b) r} \\
  \hline
  \ttt{Church' (Either a b) r} & \ttt{E (ProdMatch (Either a b) r)}\\
  \hline
\end{tabular}
}
